Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-02-01 src/tex/ms.tex
draft something on atm escape

>>>>

\rev{
\subsubsection{Other mechanisms regulating habitability and abiogenesis}
Our study focuses primarily on two factors that may regulate the emergence and persistence of life on a planet: the \gls{NUV} flux and the viability of liquid water, which provide a testable framework for assessing biosignature distributions.
Of course, planetary habitability and abiogenesis depend on a broader range of physical and chemical conditions.
For one, a planet must retain an atmosphere capable of supporting liquid water and surface chemistry.
Atmospheric escape processes have been studied in detail, and their occurrence is supported by planet formation models~\citep[e.g.,][]{Owen2013,Schlichting2014a,Ginzburg2016b,Mordasini2020,Burn2024} as well as exoplanet demographics~\citep[e.g.,][]{Owen2019a,Bergsten2022,Rogers2021a}.
Population synthesis studies demonstrate that models of atmospheric escape can explain key statistical features of the observed exoplanet population~\citep{Rogers2020,Emsenhuber2021b,Schlecker2021b,Burn2024}.}

\rev{
Planets around M~dwarfs, in particular, may be subject to significant atmospheric loss due to the extended high-luminosity pre-main-sequence phase of their host stars~\citep[e.g.,][]{Luger2015}.
%During this period, extreme X-ray and UV irradiation can drive rapid hydrodynamic escape, potentially stripping a planet of its primordial atmosphere before abiogenesis can occur.
%Even after this early phase, M-dwarf planets remain exposed to intense stellar activity, leading to further erosion of secondary atmospheres if not replenished through volcanic outgassing or other mechanisms.
Recent works~\citep[e.g.,][]{ParkCoy2024,Luque2024} interpret JWST eclipse measurements as growing evidence for the absence of substantial atmospheres on M-dwarf rocky exoplanets.
If these planets indeed lack atmospheres, their habitability would be primarily dictated by the rate of atmospheric escape~\citep[e.g.,][]{Owen2020}.
However, alternative interpretations remain viable: \citet{Ducrot2024} and \citet{Hammond2025} recently demonstrated that current JWST data cannot definitively distinguish between a bare-rock scenario and an atmosphere composed primarily of N$_2$-CO$_2$-H$_2$O.
This underscores the need for future observations and modeling efforts to constrain atmospheric retention and escape processes more robustly.}
...

%For instance, atmospheric escape processes may play a critical role not only in maintaining a planet's atmosphere but also in regulating the planet's water inventory and the availability of volatile elements for prebiotic chemistry.

\rev{While not modeled here, the above additional mechanisms may offer directions for future work.}
